The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-08-04 paper/paper.Rmd
Update paper

# Set output width
options(
  width = 72, 
  # Decimal precision
  digits = 3, 
  # Number of rows for tibble printing
  tibble.print_max = 5, 
  tibble.print_min = 5
)
```

@@

```{r}
growth_scbi <- growth_scbi %>% 
  left_join(sp_info, by = "sp")
```

@@

```{r scbi-focal-vs-comp}
focal_vs_comp_scbi <- growth_scbi %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_scbi, id = "stemID")
focal_vs_comp_scbi %>% 
  select(focal_ID, focal_sp, geometry, growth, comp)
```

@@

```{r appendix1-code, eval = FALSE, cache = FALSE}
library(tidyverse)
library(lubridate)
library(here)
library(sf)
library(viridis)
library(forestecology)
library(blockCV)
library(tictoc)

@@

growth_scbi <-
  compute_growth(
    census_1 = census_2013_scbi,
    census_2 = census_2018_scbi %>% filter(!str_detect(codes, "R")),
    id = "stemID"
  )

@@

# Compute focal versus competitor tree information ---------------------
focal_vs_comp_scbi <- growth_scbi %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_scbi, id = "stemID")

@@

growth_scbi <-
  compute_growth(
    census_1 = census_2013_scbi,
    census_2 = census_2018_scbi %>% filter(!str_detect(codes, "R")),
    id = "stemID"
  ) %>%
  # make all species the same, needs to be factor with at least two levels
  mutate(sp = factor('A', levels = c('A', 'B')) )

@@

  focal_vs_comp_scbi <- growth_scbi %>%
    create_focal_vs_comp(comp_dist = comp_dist, blocks = blocks_scbi, id = "stemID") %>%
    run_cv(comp_dist = comp_dist, blocks = blocks_scbi)

>>>>

# Set output width
options(
  width = 72, 
  # Decimal precision
  digits = 3, 
  # Number of rows for tibble printing
  tibble.print_max = 5, 
  tibble.print_min = 5
)

# TODO:
setwd("~/Documents/forestecology/forestecology/paper/")

# TODO: set eval=TRUE for Appendix code blocks
```

@@

```{r}
growth_scbi <- growth_scbi %>% 
  left_join(sp_info, by = "sp") %>% 
  # TODO:
  mutate(sp = as.factor(sp))
```

@@

```{r scbi-focal-vs-comp}
focal_vs_comp_scbi <- growth_scbi %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_scbi, id = "stemID", comp_x_var = "basal_area")
focal_vs_comp_scbi %>% 
  select(focal_ID, focal_sp, geometry, growth, comp)
```

@@

```{r appendix1-code, eval = FALSE}
library(tidyverse)
library(lubridate)
library(here)
library(sf)
library(viridis)
library(forestecology)
library(blockCV)
library(tictoc)

@@

growth_scbi <-
  compute_growth(
    census_1 = census_2013_scbi,
    census_2 = census_2018_scbi %>% filter(!str_detect(codes, "R")),
    id = "stemID"
  ) %>% 
  # Compute basal area:
  mutate(basal_area = 0.0001 * pi * (dbh1 / 2)^2)

@@

# Compute focal versus competitor tree information ---------------------
focal_vs_comp_scbi <- growth_scbi %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_scbi, id = "stemID", comp_x_var = "basal_area")

@@

growth_scbi <-
  compute_growth(
    census_1 = census_2013_scbi,
    census_2 = census_2018_scbi %>% filter(!str_detect(codes, "R")),
    id = "stemID"
  ) %>%
  # make all species the same, needs to be factor with at least two levels
  mutate(sp = factor('A', levels = c('A', 'B')) ) %>% 
  # Compute basal area:
  mutate(basal_area = 0.0001 * pi * (dbh1 / 2)^2)

@@

  focal_vs_comp_scbi <- growth_scbi %>%
    create_focal_vs_comp(comp_dist = comp_dist, blocks = blocks_scbi, id = "stemID", comp_x_var = "basal_area") %>%
    run_cv(comp_dist = comp_dist, blocks = blocks_scbi)
